---
title: "Untitled"
output: pdf_document
date: "2024-04-23"
---

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(rFIA)
library(fitdistrplus)
library(nls2)
library(minpack.lm)
```





```{r}
states_FIA <- readFIA(dir = "C:/Users/lagoodal/Desktop/Dissertation Stuff/5 States LAI/LAI")
trees <- states_FIA$TREE
seedlings <- states_FIA$SEEDLING
sp_ref <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/USDA Plant Codes.csv")
sp_ref <- sp_ref %>%
  mutate(`Synonym Symbol` = ifelse(is.na(`Synonym Symbol`), Symbol, `Synonym Symbol`))
```


```{r}
hardwoods <- seq(25,43,1)
softwoods <- seq(1,9,1)
hardwood.S <- c(0.75,0.81,0.74,0.77,0.77,0.83,0.86,0.83,0.88,0.82,0.83,0.82,0.795,0.88,0.9,0.91,0.861,0.78,0.833)
SPGRPCDs <- c(1,2,3,4,5,6,7,8,9,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43)
SPGRPs<-c("longleaf_and_slash_pines","loblolly_pines","other_yellow_pines","eastern_white_and_red_pines","Jack_pine","spruce_and_balsam_fir","eastern_hemlock","cypress","other_softwoods","white_oaks_1","red_oaks_1","white_oaks_2","red_oaks_2","hickory","yellow_birch","hard_maples","soft_maples","beech","sweetgum","tupelo","ash","cottonwood_and_aspen","basswood","yellow-poplars","black_walnut","other_eastern_soft_hardwoods","other_easter_hard_hardwoods","eastern_noncommerical_hardwoods")
SPGRPCDs.index <- seq(from = 1, to = length(SPGRPCDs))
S.table <- cbind(hardwoods, hardwood.S) %>% as.data.frame()
colnames(S.table) <- c("SPGRPCD", "Model.S")


# Calculate leaf area per tree

trees$DIA.CM <- trees$DIA * 2.54
trees$HT.M <- trees$HT / 3.2808
trees$PLOT.YEAR <- paste(trees$PLT_CN, trees$INVYR, sep=".")
trees <- trees[trees$STATUSCD == 1,]
trees.HARDWOOD <- trees[trees$SPGRPCD %in% hardwoods,]
trees.HARDWOOD <- merge(trees.HARDWOOD, S.table)
trees.HARDWOOD$LEAF.AREA.LN <- 0.2102 + (0.0586*trees.HARDWOOD$DIA.CM) + (4.0202*trees.HARDWOOD$Model.S)
trees.HARDWOOD$LEAF.AREA <- exp(trees.HARDWOOD$LEAF.AREA.LN)
SAPPS.PLOT.HARDWOOD.LEAFAREA <- aggregate(trees.HARDWOOD$LEAF.AREA, by=list(PLOT.YEAR=trees.HARDWOOD$PLOT.YEAR), FUN=sum)
colnames(SAPPS.PLOT.HARDWOOD.LEAFAREA) <- c("PLOT.YEAR","HARDWOOD.LEAFAREA")
trees.SOFTWOOD <- trees[trees$SPGRPCD %in% softwoods,]
trees.SOFTWOOD$LEAF.BIOMASS.KG <- 0.0621*(trees.SOFTWOOD$DIA.CM^1.505)
trees.SOFTWOOD$LEAF.BIOMASS.G <- trees.SOFTWOOD$LEAF.BIOMASS.KG * 1000
trees.SOFTWOOD$SURFACEAREA.TOTAL <- trees.SOFTWOOD$LEAF.BIOMASS.G / 227
trees.SOFTWOOD$SURFACEAREA.HALF <- trees.SOFTWOOD$SURFACEAREA.TOTAL / 2
SAPPS.PLOT.SOFTWOOD.LEAFAREA <- aggregate(trees.SOFTWOOD$SURFACEAREA.HALF, by=list(PLOT.YEAR=trees.SOFTWOOD$PLOT.YEAR), FUN=sum)
colnames(SAPPS.PLOT.SOFTWOOD.LEAFAREA) <- c("PLOT.YEAR","SOFTWOOD.LEAFAREA")
SAPPS.PLOT.TOTAL.LEAFAREA <- merge(SAPPS.PLOT.HARDWOOD.LEAFAREA, SAPPS.PLOT.SOFTWOOD.LEAFAREA, all=T)
SAPPS.PLOT.TOTAL.LEAFAREA[is.na(SAPPS.PLOT.TOTAL.LEAFAREA)] <- 0
SAPPS.PLOT.TOTAL.LEAFAREA$TOTAL.LEAFAREA <- SAPPS.PLOT.TOTAL.LEAFAREA$HARDWOOD.LEAFAREA + SAPPS.PLOT.TOTAL.LEAFAREA$SOFTWOOD.LEAFAREA
SAPPS.PLOT.TOTAL.LEAFAREA$PLOT.LAI <- SAPPS.PLOT.TOTAL.LEAFAREA$TOTAL.LEAFAREA / 672.469876708172
seedlings$PLOT.YEAR <- paste(seedlings$PLT_CN, seedlings$INVYR, sep=".")

# Species that we want
spp_to_use <- c("ACRU","BENI","CAGL8","CATO6","FAGR","FRAM2","FRPE","JUNI","JUVI","LIST","LITU","NYSY","OXAR","PIEC","PIST","PITA","PIVI2","PLOC","PRSE2","QUAL","QUCO2","QUFA","QUMO4","QUPH","QURU","QUST","QUVE","ULAL","ULAM","PIEL","PIPA","QUNI","QULA3","TAAS","TADI2")
spcd_to_use <- c(316,373,403,409,531,541,544,602,68,611,621,693,711,110,129,131,132,731,762,802,806,812,832,831,833,835,837,971,972,111,121,820,827,221,222)

for (i in 1:length(spcd_to_use)){
  SPCD <- spcd_to_use[i]
  Table <- seedlings[seedlings$SPCD == SPCD,]
  
  if(nrow(Table) == 0) next
  Sums <- aggregate(Table$TREECOUNT, by = list(PLOT.YEAR = Table$PLOT.YEAR), FUN = sum)
  colnames(Sums) <- c("PLOT.YEAR", spp_to_use[i])
  SAPPS.PLOT.TOTAL.LEAFAREA <- merge(SAPPS.PLOT.TOTAL.LEAFAREA, Sums, all.x = TRUE)
}

#if a species is absent from a plot, set values to 0
SAPPS.PLOT.TOTAL.LEAFAREA[is.na(SAPPS.PLOT.TOTAL.LEAFAREA)] <- 0
#only pull out plots with LAI < 20
SAPPS.PLOT.TOTAL.LEAFAREA <- SAPPS.PLOT.TOTAL.LEAFAREA[which(SAPPS.PLOT.TOTAL.LEAFAREA$PLOT.LAI < 20), ]
hist(SAPPS.PLOT.TOTAL.LEAFAREA$PLOT.LAI)


# assign seedlings to different LAI bins, depending on the plot LAI where they're
# found
mins <- seq(from=0, to= 19.8, by =0.2)
maxs <- seq(from=0.2, to = 20.0, by=0.2)
histogram.index <- seq(from=1, to=100)
SAPPS.histogram <- as.data.frame(cbind(mins, maxs))
colnames(SAPPS.histogram) <- c("min","max")



for (i in 1:length(spp_to_use)){
  SP.needed <- spp_to_use[i]
  columns.needed.vec <- c("PLOT.LAI", SP.needed)
  columns.needed <- SAPPS.PLOT.TOTAL.LEAFAREA[names(SAPPS.PLOT.TOTAL.LEAFAREA)[names(SAPPS.PLOT.TOTAL.LEAFAREA) %in% columns.needed.vec]]
  mean.inrange <- c()
  count.inrange <- c()
  for (j in histogram.index){
    min <- mins[j]
    max <- maxs[j]
    subset <- columns.needed[columns.needed$PLOT.LAI >= min & columns.needed$PLOT.LAI < max,]
    final.column <- subset[names(subset)[names(subset) %in% SP.needed]]
    final.column.vec <- as.vector(final.column)
    mean.inrange[j] <- mean(final.column[,SP.needed])
    count.inrange[j] <- sum(final.column[,SP.needed])
  }
  # SAPPS.histogram[,SP.needed] <- mean.inrange
  SAPPS.histogram[,SP.needed] <- count.inrange
}

#draw histograms for each species
for (i in 1:length(spp_to_use)){
  SP.needed <- spp_to_use[i]
  SPCD.needed <- spcd_to_use[i]
  barplot(height = SAPPS.histogram[,SP.needed], names.arg = SAPPS.histogram$max, main = SP.needed, xlab = "LAI",ylab="Seedlings/plot")
}


```



```{r}
#Fit Weibull curves to the LAI data
weibull_models <- SAPPS.PLOT.TOTAL.LEAFAREA %>%
  tidyr::pivot_longer(cols = all_of(spp_to_use),
                      names_to = "Species",
                      values_to = "Count") %>%
  group_by(Species) %>%
  filter(Count > 0) %>%
  mutate(PLOT.LAI = ifelse(PLOT.LAI < 0.01, 0.01, PLOT.LAI)) %>%
  group_by(Species) %>%
  summarise(weibull = list(fitdistr(PLOT.LAI, "weibull")))


weibull_models %>%
  mutate(shape = map_dbl(.x = .$weibull, .f = ~ pluck(.x, "estimate", "shape")),
         scale = map_dbl(.x = .$weibull, .f = ~ pluck(.x, "estimate", "scale"))) %>%
  dplyr::select(-c(weibull))



#plot the histogram and weibull fit for each species
pdf(file = "Weibull LAI distribution by species.pdf")
map2(.x = weibull_models$weibull, 
     .y = weibull_models$Species, 
     .f = ~ fitdistrplus::denscomp(.x, 
                     main = .y,
                     xlab = "LAI"))
dev.off()



# Fit Weibull distributions using fitdist from fitdistrplus
weibull_models <- SAPPS.PLOT.TOTAL.LEAFAREA %>%
  pivot_longer(cols = all_of(spp_to_use),
               names_to = "Species",
               values_to = "Count") %>%
  group_by(Species) %>%
  filter(Count > 0) %>%
  mutate(PLOT.LAI = ifelse(PLOT.LAI < 0.01, 0.01, PLOT.LAI)) %>%
  summarise(weibull = list(fitdist(PLOT.LAI, "weibull")))


# Plot the histogram and Weibull fit for each species
pdf(file = "Weibull LAI distribution by species.pdf")
map2(.x = weibull_models$weibull, 
     .y = weibull_models$Species, 
     .f = ~ denscomp(.x, 
                     main = .y,
                     xlab = "LAI"))
dev.off()


weibull_models %>%
  mutate(shape = map_dbl(.x = .$weibull, .f = ~ pluck(.x, "estimate", "shape")),
         scale = map_dbl(.x = .$weibull, .f = ~ pluck(.x, "estimate", "scale"))) %>%
  dplyr::select(-c(weibull))



x <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/Small Landscape/Clipped Piedmont/ecoregions.tif")
plot(x)
x <- ifel(x == 2, x, NA)
plot(x)
```



```{r}
states_FIA <- readFIA(dir = "C:/Users/lagoodal/Desktop/Dissertation Stuff/5 States LAI/LAI")
trees <- states_FIA$TREE
plot <- states_FIA$PLOT
cond <- states_FIA$COND
seedlings <- states_FIA$SEEDLING
sp_ref <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/USDA Plant Codes.csv")
sp_ref <- sp_ref %>% mutate(`Synonym Symbol` = ifelse(is.na(`Synonym Symbol`), Symbol, `Synonym Symbol`))

rm(states_FIA)
gc()

# Filter the plots that we will need
cond_to_use <- cond %>%
  filter(!(DSTRBCD1 %in% c(30,31,32,46,53,54,80)),
         !(DSTRBCD2 %in% c(30,31,32,46,53,54,80)),
         !(DSTRBCD3 %in% c(30,31,32,46,53,54,80)),
         TRTCD1 == 0 | is.na(TRTCD1),
         TRTCD2 == 0 | is.na(TRTCD2),
         TRTCD3 == 0 | is.na(TRTCD3)) %>%
  mutate(IS_FOREST = ifelse(FORTYPCD %in%(c(1:998)), 1, 0)) %>%
  group_by(PLT_CN) %>%
  summarise(total_cond = sum(CONDPROP_UNADJ),
            natural = sum(STDORGCD, na.rm = TRUE),
            treatment = sum(TRTCD1, na.rm = TRUE),
            proportion_forest = sum(CONDPROP_UNADJ * IS_FOREST)) %>%
  filter(total_cond > 0.95,
         proportion_forest > 0.95)
plots_to_use <- plot %>%
  dplyr::filter(PLOT_STATUS_CD == 1) %>%
  left_join(cond_to_use, by = c("CN" = "PLT_CN")) %>%
  dplyr::select(CN, proportion_forest)

#------------------------------------------------
# Crosswalk LANDIS and FIA species codes
#------------------------------------------------

func_table <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/clippedTest_NECN_Functional_Table.csv")
sp_table <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/speciesParameters.csv") %>%
  left_join(func_table, by = "FunctionalGroupIndex")

# sp_table$SpeciesCode <- c("JUVI","QUPH","ULAL","ULAM","PIST","ACRU","LITU","QUMO4","PIVI2","PITA","CAGL8","PIEC","BENI","CATO6","FAGR","FRAM2","FRPE","JUNI","LIST","NYSY","OXAR","PLOC","PRSE2","QUAL","QUCO2","QUFA","QURU","QUST","QUVE","PIPA2")

#we need to assign each species group a value for KLAI and MaximumLAI
spgrp_lai <- data.frame(SPGRPCD = unique(trees$SPGRPCD),
                        FunctionalGroupIndex = numeric(length(unique(trees$SPGRPCD)))) %>%
  arrange(SPGRPCD) %>%
  mutate(FunctionalGroupIndex = ifelse(SPGRPCD %in% c(1:24), 1, FunctionalGroupIndex))%>%
  mutate(FunctionalGroupIndex = ifelse(SPGRPCD %in% c(25:47), 2, FunctionalGroupIndex))%>%
  mutate(FunctionalGroupIndex = ifelse(SPGRPCD %in% c(17,18), 4, FunctionalGroupIndex))%>%
  mutate(FunctionalGroupIndex = ifelse(SPGRPCD %in% c(48), 3, FunctionalGroupIndex)) %>%
  left_join(func_table %>% dplyr::select(FunctionalGroupIndex, KLAI, MaximumLAI))

SpeciesCode <- c("JUVI","QUPH","ULAL","ULAM","PIST","ACRU","LITU","QUMO4","PIVI2","PITA","CAGL8","PIEC","BENI","CATO6","FAGR","FRAM2","FRPE","JUNI","LIST","NYSY","OXAR","PLOC","PRSE2","QUAL","QUCO2","QUFA","QURU","QUST","QUVE","PIPA")
SPCD <- c(68,831,971,972,129,316,621,832,132,131,403,110,373,409,531,541,544,602,611,693,711,731,762,802,806,812,833,835,837,122)
spp_crosswalk <- as.data.frame(SpeciesCode) %>% cbind(., as.data.frame(SPCD))




fitdist()

```


# Thats just a regression model to estimate age from diameter. I dont think the models I have will work for you, since theyre species-specific.
# Id recommend starting with log(age) ~ log(diam) + (1|species) for starters; that will give you a power-law relationship with a random effect for the coefficient and a shared exponent. But other functional forms might work better for your species.




spp_to_use <- spp_crosswalk$SpeciesCode
spcd_to_use <- spp_crosswalk$SPCD
all_spcd <- unique(trees$SPCD)



trees <- trees %>%
  mutate(PLOT.YEAR = paste(PLT_CN, INVYR, sep=".")) %>%
  right_join(., plots_to_use, by = c("PLT_CN" = "CN")) %>%
    dplyr::mutate(DIA_cm = DIA * 2.54,
                  HT_m = HT / 3.3808,
                  PLOT.YEAR = paste(PLT_CN, INVYR, sep=".")) %>%
    dplyr::filter(STATUSCD == 1) %>%
    dplyr::left_join(spgrp_lai)


sort(names(trees))

age_model <- lme4::lmer(log(TOTAGE) ~ log(DIA) + (1|species), data = trees[!is.na(trees$DIA) & !is.na(trees$TOTAGE), ])
age_model2 <- lm(log(TOTAGE) ~ poly(log(DIA), 3), data = trees[!is.na(trees$DIA) & !is.na(trees$TOTAGE), ])


install.packages("lme4")


sp_ref %>% filter(`Common Name` == "longleaf pine")







```{r}
states_FIA <- readFIA(dir = "C:/Users/lagoodal/Desktop/Dissertation Stuff/5 States LAI/LAI")
trees <- states_FIA$TREE
plot <- states_FIA$PLOT
cond <- states_FIA$COND
seedlings <- states_FIA$SEEDLING
sp_ref <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/USDA Plant Codes.csv")
sp_ref <- sp_ref %>% mutate(`Synonym Symbol` = ifelse(is.na(`Synonym Symbol`), Symbol, `Synonym Symbol`))

rm(states_FIA)
gc()

# Filter out plots that have been recently treated or not in the forest anymore
cond_to_use <- cond %>%
  filter(!(DSTRBCD1 %in% c(30,31,32,46,53,54,80)),
         !(DSTRBCD2 %in% c(30,31,32,46,53,54,80)),
         !(DSTRBCD3 %in% c(30,31,32,46,53,54,80)),
         TRTCD1 == 0 | is.na(TRTCD1),
         TRTCD2 == 0 | is.na(TRTCD2),
         TRTCD3 == 0 | is.na(TRTCD3)) %>%
  mutate(IS_FOREST = ifelse(FORTYPCD %in%(c(1:998)), 1, 0)) %>%
  group_by(PLT_CN) %>%
  summarise(total_cond = sum(CONDPROP_UNADJ),
            natural = sum(STDORGCD, na.rm = TRUE),
            treatment = sum(TRTCD1, na.rm = TRUE),
            proportion_forest = sum(CONDPROP_UNADJ * IS_FOREST)) %>%
  filter(total_cond > 0.95,
         proportion_forest > 0.95)

plots_to_use <- plot %>%
  filter(PLOT_STATUS_CD == 1) %>%
  left_join(cond_to_use, by = c("CN" = "PLT_CN")) %>%
  dplyr::select(CN, proportion_forest)


group_ref_shade <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/5 States LAI/REF_SPECIES_GROUP_SHADE.csv")

# Calculate leaf area
trees <- trees %>%
  right_join(., plots_to_use, by = c("PLT_CN" = "CN")) %>%
  dplyr::mutate(DIA_cm = DIA * 2.54,
                HT_m = HT / 3.3808,
                PLOT.YEAR = paste(PLT_CN, INVYR, sep=".")) %>%
  dplyr::filter(STATUSCD == 1) %>%
  dplyr::left_join((group_ref_shade %>% dplyr::select(SPGRPCD, ShadeCoef_iTree))) %>%
  #shade factor equation from iTree
  dplyr::mutate(ShadeFactor = 0.0617 * log(DIA_cm) + 0.615 + ShadeCoef_iTree,
                CrownHeight = HT_m * CR/100,
                CrownWidth =  0.8304 + 27.82 * (DIA_cm/100) - 10.68 * ((DIA_cm/100)^2),
                CrownWidth = ifelse(DIA_cm > 100, 20, CrownWidth),
                HWR = CrownHeight / CrownWidth) %>% 
  # equation for crown width from Coombes, A., J. Martin, and D. Slater. 2019. Defining the allometry of stem and crown diameter of urban trees. Urban Forestry & Urban Greening 44:126421.
  # capped at 20 m because the quadratic shape doesn't play well after that
  dplyr::mutate(LEAF.AREA = exp( -4.3309 + 0.2942 * CrownHeight + 0.7312 * CrownWidth + 
                                   5.7217 * ShadeFactor + 
                                   -0.0148 * pi * CrownWidth*(CrownHeight + CrownWidth)/2)) %>%
  #gotta do something special if the trees are too big or too small, following the iTree equations
  #sorry this code is pretty clumsy
  dplyr::mutate(LEAF.AREA = ifelse(HWR > 2.0, 
                                   exp( -4.3309 + 0.2942 * CrownHeight + 0.7312 * (CrownHeight/2) + 
                                          5.7217 * ShadeFactor + 
                                          -0.0148 * pi * (CrownHeight/2)*(CrownHeight + (CrownHeight/2))/2) *
                                     HWR/2.0,
                                   LEAF.AREA)) %>%
  dplyr::mutate(LEAF.AREA = ifelse(HWR < 0.5,
                                   exp( -4.3309 + 0.2942 * CrownHeight + 0.7312 * (CrownHeight*2) + 
                                          5.7217 * ShadeFactor + 
                                          -0.0148 * pi * (CrownHeight*2)*(CrownHeight + (CrownHeight*2))/2) *
                                     0.5/HWR,
                                   LEAF.AREA))

# Now leaf area per plot
plot_leaf_area <- trees %>%
  group_by(PLOT.YEAR) %>%
  #m2 per tree * trees per acre * acre per m2 = meters squared leaf area per meter squared ground
  summarise(LAI = sum(LEAF.AREA*TPA_UNADJ/4046, na.rm = TRUE)) %>% 
  filter(!is.na(LAI) & !is.infinite(LAI)) %>%
  filter(LAI < 20)

mean(plot_leaf_area$LAI)
hist(plot_leaf_area$LAI)
mean_lai_desired <- 3
plot_leaf_area <- plot_leaf_area %>%
  mutate(LAI = LAI * mean_lai_desired/mean(LAI, na.rm = TRUE))
hist(plot_leaf_area$LAI)

# Get Seedlings
seedlings <- seedlings %>%
  mutate(PLOT.YEAR = paste(PLT_CN, INVYR, sep="."),
         TPA_UNADJ = ifelse(is.na(TPA_UNADJ), 0, TPA_UNADJ)) %>%
  filter(PLOT.YEAR %in% plot_leaf_area$PLOT.YEAR) %>%
  # filter(TOTAGE <= 5) %>% #only useful in RMRS zone, and only collected fora  subset of trees
  group_by(PLOT.YEAR) %>%
  mutate(SEEDLING_COUNT = sum(TPA_UNADJ)) %>%
  slice_head(n = 1)

# Species that we want to model
SpeciesCode <- c("JUVI","QUPH","ULAL","ULAM","PIST","ACRU","LITU","QUMO4","PIVI2","PITA","CAGL8","PIEC","BENI","CATO6","FAGR","FRAM2","FRPE","JUNI","LIST","NYSY","OXAR","PLOC","PRSE2","QUAL","QUCO2","QUFA","QURU","QUST","QUVE")
SPCD <- c(68,831,971,972,129,316,621,832,132,131,403,110,373,409,531,541,544,602,611,693,711,731,762,802,806,812,833,835,837)
spp_crosswalk <- as.data.frame(SpeciesCode) %>% cbind(., as.data.frame(SPCD))
spp_to_use <- spp_crosswalk$SpeciesCode

# Find how many seedlings are in each plot
for (i in 1:nrow(spp_crosswalk)){
  SPCD <- spp_crosswalk[[i, "SPCD"]][[1]]
  Table <- seedlings[seedlings$SPCD %in% SPCD,]
  
  if(nrow(Table) == 0) next #this breaks the rest of the code, because further down expects a column for every species
  
  Sums <- aggregate(Table$TREECOUNT, by=list(PLOT.YEAR = Table$PLOT.YEAR), FUN=sum)
  Sums$x <- ifelse(is.na(Sums$x), 0, Sums$x)
  
  colnames(Sums) <- c("PLOT.YEAR", spp_to_use[i])
  plot_leaf_area <- left_join(plot_leaf_area, Sums, by = "PLOT.YEAR")
}

plot_leaf_area <- plot_leaf_area %>%
  mutate(across(where(is.numeric), ~ ifelse(is.na(.), 0, .)))

n_seedlings <- plot_leaf_area %>%
               tidyr::pivot_longer(cols = all_of(spp_to_use),
                        names_to = "Species",
                        values_to = "Count") %>%
  group_by(Species) %>%
  summarize(total = sum(Count))

# this is more appropriate as a method -- we want to fit p(seedling | LAI),
# so we need to standardize by the number of plots in each LAI bin

#make histogram for proportion
nBins <- 20
minLAI <- 0.1
plot_seedling_histogram <- plot_leaf_area %>%
  tidyr::pivot_longer(cols = all_of(spp_to_use),
                      names_to = "Species",
                      values_to = "Count") %>%
  mutate(LAI = ifelse(LAI < minLAI, minLAI, LAI)) %>%
  mutate(lai_bin = base::cut(LAI, breaks = nBins),
         present = ifelse(Count>0, 1, 0)) %>%
  group_by(Species, lai_bin) %>%
  summarise(n_present = sum(present),
            n_plots_bin = n(),
            prop_present = n_present / n_plots_bin) %>%
  ungroup() %>%
  group_by(Species) %>%
  mutate(prop_present = prop_present / sum(prop_present)) %>% #proportion of plots in the bin with seedlings
  mutate(lai = strsplit(as.character(lai_bin), split = ",") %>% #calculate the midpoint of the bin
           map(., .f = ~gsub("\\(|\\]", "", .)) %>%
           map(pluck(1)) %>% #actually, we should use the left side of the bin, not zero -- otherwise
                              # we all the distributions having no regen at LAI = 0
           # map(., .f = ~mean(as.numeric(.))) %>%
           unlist() %>%
           as.numeric())
```



























