---
title: "Untitled"
output: pdf_document
date: "2025-02-14"
---


```{r}
library(tidyverse)
```


```{r}
#----SUCCESSION LOG----#
successionLog <- rbind(successionLog_BNU_ESM_RCP45_Resilience,
                       successionLog_BNU_ESM_RCP45_Resistance,
                       successionLog_BNU_ESM_RCP45_Transition,
                       successionLog_BNU_ESM_RCP85_Resilience,
                       successionLog_BNU_ESM_RCP85_Resistance,
                       successionLog_BNU_ESM_RCP85_Transition,
                       successionLog_CCSM4_RCP45_Resilience,
                       successionLog_CCSM4_RCP45_Resistance,
                       successionLog_CCSM4_RCP45_Transition,
                       successionLog_CCSM4_RCP85_Resilience,
                       successionLog_CCSM4_RCP85_Resistance,
                       successionLog_CCSM4_RCP85_Transition,
                       successionLog_MIROC_ESM_CHEM_RCP45_Resilience,
                       successionLog_MIROC_ESM_CHEM_RCP45_Resistance,
                       successionLog_MIROC_ESM_CHEM_RCP45_Transition,
                       successionLog_MIROC_ESM_CHEM_RCP85_Resilience,
                       successionLog_MIROC_ESM_CHEM_RCP85_Resistance,
                       successionLog_MIROC_ESM_CHEM_RCP85_Transition,
                       successionLog_MRI_CGCM3_RCP45_Resilience,
                       successionLog_MRI_CGCM3_RCP45_Resistance,
                       successionLog_MRI_CGCM3_RCP45_Transition,
                       successionLog_MRI_CGCM3_RCP85_Resilience,
                       successionLog_MRI_CGCM3_RCP85_Resistance,
                       successionLog_MRI_CGCM3_RCP85_Transition) %>%
  filter(Time < 81) %>%
  select(-ClimateRegionIndex, -NumSites)

x <- successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time != 0) %>%
  mutate(ANPP = (AG_NPPC + BG_NPPC) * 2)
summary(aov(AGB ~ RCP * Model * Prescription, data = x))


# NEEC
successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = Time, y = NEEC, col = Model)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(RCP ~ Prescription) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100))

# SOMTC
successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = Time, y = SOMTC, col = Model)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  ylim(2400,4000) +
  geom_hline(yintercept = 3000, linetype = "dashed") +
  facet_grid(RCP ~ Prescription) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  scale_y_continuous(name = "SOMTC g/m2")

# NPP
successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model),
         NPP = (AG_NPPC + BG_NPPC) * 2) %>%
  filter(Time != 0) %>%
  ggplot(., aes(x = Time, y = NPP, col = Model)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(RCP ~ Prescription) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Total Net Primary Productivity")

successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model),
         NPP = (AG_NPPC + BG_NPPC) * 2) %>%
  filter(Time != 0) %>%
  ggplot(., aes(x = Time, y = NPP, col = Prescription)) +
  geom_line(alpha = 0, size = 1.5) +
  geom_hline(yintercept = 750) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  geom_smooth(se = FALSE) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Total Net Primary Productivity")

successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model),
         NPP = (AG_NPPC + BG_NPPC) * 2) %>%
  filter(Time != 0) %>%
  ggplot(., aes(x = Time, y = NPP, col = RCP)) +
  geom_line(alpha = 0, size = 1.5) +
  theme_classic() +
  facet_grid(Prescription ~ Model) +
  geom_smooth(se = FALSE) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Total Net Primary Productivity")


successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model),
         NPP = (AG_NPPC + BG_NPPC) * 2) %>%
  filter(Time != 0) %>%
  select(Time, NPP, Prescription, RCP, Model) %>%
  arrange(desc(NPP))

# TotalN
successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = Time, y = TotalN, col = Model)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(RCP ~ Prescription) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Total N")

# Age Mortality
successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = Time, y = AgeMortality, col = Model)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(RCP ~ Prescription) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Senesced Biomass (g/m2)")

successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = Time, y = AgeMortality, col = Prescription)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Senesced Biomass (g/m2)")

successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = Time, y = AgeMortality, col = RCP)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(Prescription ~ Model) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Senesced Biomass (g/m2)")

# Litterfall
successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = Time, y = Litterfall, col = Model)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(RCP ~ Prescription) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Litterfall (g/m2)")

successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = Time, y = Litterfall, col = Prescription)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Litterfall (g/m2)")

successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time != 0) %>%
  ggplot(., aes(x = Time, y = Litterfall, col = RCP)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(Model ~ Prescription) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  ylab("Litterfall (g/m2)")

# Aboveground Biomass
successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time != 0) %>%
  ggplot(., aes(x = Time, y = AGB, col = Model)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(RCP ~ Prescription) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  scale_y_continuous(name = "AGB (kg/m2)", breaks = c(8e3,1e4,1.2e4), labels = c(8,10,12))

successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time != 0) %>%
  ggplot(., aes(x = Time, y = AGB, col = Prescription)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  scale_y_continuous(name = "AGB (kg/m2)", breaks = c(8e3,1e4,1.2e4), labels = c(8,10,12))

successionLog %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time != 0) %>%
  ggplot(., aes(x = Time, y = AGB, col = RCP)) +
  geom_line(alpha = 1, size = 1.5) +
  theme_classic() +
  facet_grid(Model ~ Prescription) +
  scale_x_continuous(name = "Year", breaks = c(0,20,40,60,80), labels = c(2020,2040,2060,2080,2100)) +
  scale_y_continuous(name = "AGB (kg/m2)", breaks = c(8e3,1e4,1.2e4), labels = c(8,10,12))

#----DIVERSITY----#
diversityDf <- rbind(diversity_BNU_ESM_RCP45_Resilience,
      diversity_BNU_ESM_RCP45_Resistance,
      diversity_BNU_ESM_RCP45_Transition,
      diversity_BNU_ESM_RCP85_Resilience,
      diversity_BNU_ESM_RCP85_Resistance,
      diversity_BNU_ESM_RCP85_Transition,
      diversity_CCSM4_RCP45_Resilience,
      diversity_CCSM4_RCP45_Resistance,
      diversity_CCSM4_RCP45_Transition,
      diversity_CCSM4_RCP85_Resilience,
      diversity_CCSM4_RCP85_Resistance,
      diversity_CCSM4_RCP85_Transition,
      diversity_MIROC_ESM_CHEM_RCP45_Resilience,
      diversity_MIROC_ESM_CHEM_RCP45_Resistance,
      diversity_MIROC_ESM_CHEM_RCP45_Transition,
      diversity_MIROC_ESM_CHEM_RCP85_Resilience,
      diversity_MIROC_ESM_CHEM_RCP85_Resistance,
      diversity_MIROC_ESM_CHEM_RCP85_Transition,
      diversity_MRI_CGCM3_RCP45_Resilience,
      diversity_MRI_CGCM3_RCP45_Resistance,
      diversity_MRI_CGCM3_RCP45_Transition,
      diversity_MRI_CGCM3_RCP85_Resilience,
      diversity_MRI_CGCM3_RCP85_Resistance,
      diversity_MRI_CGCM3_RCP85_Transition)

diversityDf %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time < 81 & Time > 0) %>%
  ggplot(., aes(x = Time, y = H, col = Model)) +
  geom_line(size = 2) +
  theme_classic() +
  facet_grid(RCP ~ Prescription)

diversityDf %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time < 81 & Time > 0) %>%
  ggplot(., aes(x = Time, y = H, col = Prescription)) +
  geom_line(size = 2) +
  theme_classic() +
  facet_grid(RCP ~ Model)

diversityDf %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time < 81 & Time > 0) %>%
  ggplot(., aes(x = Time, y = H, col = RCP)) +
  geom_line(size = 2) +
  theme_classic() +
  facet_grid(Model ~ Prescription)

diversityDf %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time < 81 & Time > 0) %>%
  aov(H ~ Model * RCP * Prescription, data = .) %>%
  summary(.)

diversityDf %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  filter(Time < 81 & Time > 0) %>%
  arrange(desc(H))

```

#----ANNUAL WATER BUDGET----#
rbind(AWB_BNU_ESM_RCP45_ResistanceDf,
      AWB_BNU_ESM_RCP45_ResilienceDf,
      AWB_BNU_ESM_RCP45_TransitionDf,
      AWB_BNU_ESM_RCP85_ResistanceDf,
      AWB_BNU_ESM_RCP85_ResilienceDf,
      AWB_BNU_ESM_RCP85_TransitionDf,
      AWB_CCSM4_RCP45_ResistanceDf,
      AWB_CCSM4_RCP45_ResilienceDf,
      AWB_CCSM4_RCP45_TransitionDf,
      AWB_CCSM4_RCP85_ResistanceDf,
      AWB_CCSM4_RCP85_ResilienceDf,
      AWB_CCSM4_RCP85_TransitionDf,
      AWB_MIROC_ESM_CHEM_RCP45_ResistanceDf,
      AWB_MIROC_ESM_CHEM_RCP45_ResilienceDf,
      AWB_MIROC_ESM_CHEM_RCP45_TransitionDf,
      AWB_MIROC_ESM_CHEM_RCP85_ResistanceDf,
      AWB_MIROC_ESM_CHEM_RCP85_ResilienceDf,
      AWB_MIROC_ESM_CHEM_RCP85_TransitionDf,
      AWB_MRI_CGCM3_RCP45_ResistanceDf,
      AWB_MRI_CGCM3_RCP45_ResilienceDf,
      AWB_MRI_CGCM3_RCP45_TransitionDf,
      AWB_MRI_CGCM3_RCP85_ResistanceDf,
      AWB_MRI_CGCM3_RCP85_ResilienceDf,
      AWB_MRI_CGCM3_RCP85_TransitionDf) %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = as.integer(Time), y = AWB, col = Model)) +
  geom_line(size = 2) +
  theme_classic() +
  facet_grid(RCP ~ Prescription)

rbind(AWB_BNU_ESM_RCP45_ResistanceDf,
      AWB_BNU_ESM_RCP45_ResilienceDf,
      AWB_BNU_ESM_RCP45_TransitionDf,
      AWB_BNU_ESM_RCP85_ResistanceDf,
      AWB_BNU_ESM_RCP85_ResilienceDf,
      AWB_BNU_ESM_RCP85_TransitionDf,
      AWB_CCSM4_RCP45_ResistanceDf,
      AWB_CCSM4_RCP45_ResilienceDf,
      AWB_CCSM4_RCP45_TransitionDf,
      AWB_CCSM4_RCP85_ResistanceDf,
      AWB_CCSM4_RCP85_ResilienceDf,
      AWB_CCSM4_RCP85_TransitionDf,
      AWB_MIROC_ESM_CHEM_RCP45_ResistanceDf,
      AWB_MIROC_ESM_CHEM_RCP45_ResilienceDf,
      AWB_MIROC_ESM_CHEM_RCP45_TransitionDf,
      AWB_MIROC_ESM_CHEM_RCP85_ResistanceDf,
      AWB_MIROC_ESM_CHEM_RCP85_ResilienceDf,
      AWB_MIROC_ESM_CHEM_RCP85_TransitionDf,
      AWB_MRI_CGCM3_RCP45_ResistanceDf,
      AWB_MRI_CGCM3_RCP45_ResilienceDf,
      AWB_MRI_CGCM3_RCP45_TransitionDf,
      AWB_MRI_CGCM3_RCP85_ResistanceDf,
      AWB_MRI_CGCM3_RCP85_ResilienceDf,
      AWB_MRI_CGCM3_RCP85_TransitionDf) %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = as.integer(Time), y = AWB, col = RCP)) +
  geom_line(size = 2) +
  theme_classic() +
  facet_grid(Model ~ Prescription)

rbind(AWB_BNU_ESM_RCP45_ResistanceDf,
      AWB_BNU_ESM_RCP45_ResilienceDf,
      AWB_BNU_ESM_RCP45_TransitionDf,
      AWB_BNU_ESM_RCP85_ResistanceDf,
      AWB_BNU_ESM_RCP85_ResilienceDf,
      AWB_BNU_ESM_RCP85_TransitionDf,
      AWB_CCSM4_RCP45_ResistanceDf,
      AWB_CCSM4_RCP45_ResilienceDf,
      AWB_CCSM4_RCP45_TransitionDf,
      AWB_CCSM4_RCP85_ResistanceDf,
      AWB_CCSM4_RCP85_ResilienceDf,
      AWB_CCSM4_RCP85_TransitionDf,
      AWB_MIROC_ESM_CHEM_RCP45_ResistanceDf,
      AWB_MIROC_ESM_CHEM_RCP45_ResilienceDf,
      AWB_MIROC_ESM_CHEM_RCP45_TransitionDf,
      AWB_MIROC_ESM_CHEM_RCP85_ResistanceDf,
      AWB_MIROC_ESM_CHEM_RCP85_ResilienceDf,
      AWB_MIROC_ESM_CHEM_RCP85_TransitionDf,
      AWB_MRI_CGCM3_RCP45_ResistanceDf,
      AWB_MRI_CGCM3_RCP45_ResilienceDf,
      AWB_MRI_CGCM3_RCP45_TransitionDf,
      AWB_MRI_CGCM3_RCP85_ResistanceDf,
      AWB_MRI_CGCM3_RCP85_ResilienceDf,
      AWB_MRI_CGCM3_RCP85_TransitionDf) %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  ggplot(., aes(x = as.integer(Time), y = AWB, col = Prescription)) +
  geom_line(size = 2) +
  theme_classic() +
  facet_grid(Model ~ RCP)

rbind(AWB_BNU_ESM_RCP45_ResistanceDf,
      AWB_BNU_ESM_RCP45_ResilienceDf,
      AWB_BNU_ESM_RCP45_TransitionDf,
      AWB_BNU_ESM_RCP85_ResistanceDf,
      AWB_BNU_ESM_RCP85_ResilienceDf,
      AWB_BNU_ESM_RCP85_TransitionDf,
      AWB_CCSM4_RCP45_ResistanceDf,
      AWB_CCSM4_RCP45_ResilienceDf,
      AWB_CCSM4_RCP45_TransitionDf,
      AWB_CCSM4_RCP85_ResistanceDf,
      AWB_CCSM4_RCP85_ResilienceDf,
      AWB_CCSM4_RCP85_TransitionDf,
      AWB_MIROC_ESM_CHEM_RCP45_ResistanceDf,
      AWB_MIROC_ESM_CHEM_RCP45_ResilienceDf,
      AWB_MIROC_ESM_CHEM_RCP45_TransitionDf,
      AWB_MIROC_ESM_CHEM_RCP85_ResistanceDf,
      AWB_MIROC_ESM_CHEM_RCP85_ResilienceDf,
      AWB_MIROC_ESM_CHEM_RCP85_TransitionDf,
      AWB_MRI_CGCM3_RCP45_ResistanceDf,
      AWB_MRI_CGCM3_RCP45_ResilienceDf,
      AWB_MRI_CGCM3_RCP45_TransitionDf,
      AWB_MRI_CGCM3_RCP85_ResistanceDf,
      AWB_MRI_CGCM3_RCP85_ResilienceDf,
      AWB_MRI_CGCM3_RCP85_TransitionDf) %>%
  mutate(Model = sub("_[^_]+$", "", Model)) %>%
  aov(AWB ~ Model * Prescription * RCP, data = .) %>%
  summary(.)
```
















